Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-25 paper.tex
limits: 10 pages without references
modified title, as the "on Abstractions".. was incorrect.   open to further refinement.
Fix header

@@

%Conference
\acmConference[SC2017]{The International Conference for High Performance Computing, Networking, Storage and Analysis}{November 2017}{Denver, Colorado USA}
\acmYear{2017}
\copyrightyear{2017}

@@

\title{A Case Study on Abstractions to Converge High-Throughput and High-Performance Computing}

>>>>

% -----------------------------------------------------------------------------
% PAGE LIMIT
% Papers must be submitted in PDF format (readable by Adobe Acrobat Reader 5.0
% and higher) and formatted for 8.5" x 11" (U.S. Letter). Submissions are
% limited to 10 pages in the ACM format (see
% http://www.acm.org/sigs/publications/proceedings-templates), using the
% sample-sigconf template. The 10-page limit includes figures, tables, and
% appendices, but does not include references, for which there is no page limit.
% -----------------------------------------------------------------------------

@@

%Conference
\acmConference[SC2017]{The International Conference for High Performance Computing, Networking, Storage and Analysis}{Nov 2017}{Denver, Colorado}
\acmYear{2017}
\copyrightyear{2017}

@@

\title{Converging High-Throughput and High-Performance Computing: A Case Study}
